\vspace{-0.5cm}The X-shooter GTO sample of GRB afterglow and host Galaxy spectra

### 2016-09-26 document/XSGRB_sample.tex
text and table update for GRB100814A

@@

    \subsection{GRB130408A (z = 3.758)}
	The data presented here also formed the basis of GCN \#
	14365\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/14365.gcn3}}. The spectrum
	has not otherwise been published previously. The observations consists of two
	600sec spectra taken 1.9hr after the burst. We detect absorption features from
	a wide range of ions. We also detect intervening absorption at $z=1.255$ and
	$z=3.248$.

	\subsection{GRB130606A (z = 5.913)}
	The data presented here also formed the basis of GCN \#
	14816\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/14816.gcn3}} and is published
	in \citet{Hartoog2015}. The observations consists of three 2x600sec visits
	starting 7.1 hr after the burst at fairly high airmass. We detect absorption
	features from a wide range of ions at $z=5.913$ as well as intervening
	absorption at $z=2.3103, 2.5207, 3.4515, 4.4660, 4.5309, 4.5427, 4.6497 $ and $
	4.7244$.

	\subsection{GRB151021A (z = 2.330)}
	The data presented here also formed the basis of GCN \#
	18426\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/18982.gcn3}} and is not
	published elsewhere. The observation was carried out in RRM starting 44 min af
	the GRB trigger. We detect absorption features from a wide range of ions at
	$z=2.330$ as well as intervening absorption at $z=1.49$.

	\subsection{GRB160203A (z = 3.517)}
	The data presented here also formed the basis of GCN \#
	18982\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/18982.gcn3}} and is not
	published elsewhere. The observation was carried out in RRM starting 18 min
	after the GRB trigger. We detect absorption features from a wide range of ions
	at $z=3.517$ as well as intervening absorption at $z=2.203$.

>>>>

	\subsection{GRB100814A (z=1.439)}
    The spectra presented here has not been published previously. The
    observations consists of three visits, the first beginning only 0.9 hours
    after the \textit{Swift} trigger, the other two visits were 2.13 and 98.40
    hours after the trigger, respectively. A bright afterglow continuum is
    present in all visits, allowing identification of absorption features
    belonging to a wide range of ions at $z=1.439$. A complex velocity structure
    in the absorption features belonging to \mgii, shows several components,
    separated by as much as 5000km/s, pointing to a likely merger scenario in
    the host.

@@

    \subsection{GRB130408A (z = 3.758)}
	The data presented here also formed the basis of GCN \#
	14365\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/14365.gcn3}}. The spectrum
	has not otherwise been published previously. The observations consists of two
	600sec spectra taken 1.9hrs after the burst. We detect absorption features from
	a wide range of ions. We also detect intervening absorption at $z=1.255$ and
	$z=3.248$.

	\subsection{GRB130606A (z = 5.913)}
	The data presented here also formed the basis of GCN \#
	14816\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/14816.gcn3}} and is published
	in \citet{Hartoog2015}. The observations consists of three 2x600sec visits
	starting 7.1 hrs after the burst at fairly high airmass. We detect absorption
	features from a wide range of ions at $z=5.913$ as well as intervening
	absorption at $z=2.3103, 2.5207, 3.4515, 4.4660, 4.5309, 4.5427, 4.6497 $ and $
	4.7244$.

	\subsection{GRB151021A (z = 2.330)}
	The data presented here also formed the basis of GCN \#
	18426\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/18982.gcn3}} and is not
	published elsewhere. The observation was carried out in RRM starting 44 minutes
	after the GRB trigger. We detect absorption features from a wide range of ions
	at $z=2.330$ as well as intervening absorption at $z=1.49$.

	\subsection{GRB160203A (z = 3.517)}
	The data presented here also formed the basis of GCN \#
	18982\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/18982.gcn3}} and is not
	published elsewhere. The observation was carried out in RRM starting 18 minutes
	after the GRB trigger. We detect absorption features from a wide range of ions
	at $z=3.517$ as well as intervening absorption at $z=2.203$.
